DATA 621 Homework #4

### 2019-11-07 hw4/HW4.Rmd
A bit more work

>>>>

### MSTATUS

**Theoretical Effect**
In theory, married people drive more safely

```{r} 
hw4_categorical_plot(df, "MSTATUS")
hw4_target_table(df, "MSTATUS")
```

### MVR_PTS

**Theoretical Effect**
If you get lots of traffic tickets, you trend to get into more crashes

```{r} 
hw4_categorical_plot(df, "MVR_PTS")
hw4_target_table(df, "MVR_PTS")
```
